Homework # 6 UW Data Science course by rvij@cisco.com
========================================================

# Define functions used in the homework 

```{r}
setwd("/Users/rajeevvij/Documents/DOcRep/~DataScienceCisco/Module2")

# Reading data from the given files into R
readFromFiles <- function() {
  print("Read data files and print summaries")
  adultfev <<- read.csv("/Users/rajeevvij/Documents/DOcRep/~DataScienceCisco/Module2/adultfev.csv", header=T, sep=",", colClasses = c("character","integer","numeric", "numeric", "factor","factor"))
  adultfevmiss <<- read.csv("/Users/rajeevvij/Documents/DOcRep/~DataScienceCisco/Module2/adultfevmiss.csv", header=T, sep=",", colClasses = c("character","integer","numeric", "numeric", "factor","factor"))
  print(summary(adultfev))
  print(summary(adultfevmiss))
}

# Estimate the adjusted effect of smoking on fev. 
# The assumptions of linear regression that we covered in class were linearity, 
# normality of residuals, homoskedasticity of residuals, and independence of residuals.  
# Using qqplots, and boxplots of the residuals, assess these assumptions for the proposed analysis. 
# (note, one of the assumptions does not apply for a binary explanatory variable).


question1 <- function(){
  print("Perform lm and plot dignistic charts for the residuals against different variables")
  lm1 <<- lm(fev ~ smoke+height+age+male, data=adultfev)
  summarylm1 <<- summary(lm1)
  anovalm1 <<- anova(lm1)
  par(mfrow = c(2,2))
  plot(lm1)
  par(mfrow = c(2,2))
  qqplot(adultfev$smoke, lm1$resid)
  qqplot(adultfev$male, lm1$resid)
  qqplot(adultfev$age, lm1$resid)
  qqplot(adultfev$height, lm1$resid)
}


question2 <- function(){
  print("Print summary of the lm and provide details of the p-value and slopes")
  print(summarylm1)
  print(anovalm1)
}

question3 <- function(){
  print("How to address violations of the assumptions in lm")
  print("Use transformation of variables to address linearity and homoskedasticity of residuals")
  print("===========")
}

question4 <- function(){
  print("Perform lm with missing data anf complete cases")
  adultfevmissing_cc <- adultfevmiss[complete.cases(adultfevmiss),]
  lm1cc <<- lm(fev ~ smoke+height+age+male, data=adultfevmissing_cc)
  summarylm1cc <- summary(lm1cc)
  anovalm1cc <- anova(lm1cc)
  print(summarylm1cc)
  print(anovalm1cc)
}

question5 <- function(){
  print("Impute missing data using mice package and compare with complete lm")
  require(mice)
  adultfevmiss.imputed <- mice(adultfevmiss)
  
  summarylmcc <- summary(lm(fev ~ smoke+height+age+male, data=adultfevmiss))
  
  impute.fit <- with(adultfevmiss.imputed, lm(fev ~ smoke+height+age+male))
  print(summarylmcc)
  print(summary(pool(impute.fit)))
}

question6 <- function(){
  print("Calculate the power of a test")
  power08 <- power.t.test(n=300, power=0.8, sd=75)
  power09 <- power.t.test(n=300, power=0.9, sd=75)
  print(power08)
  print(power09)
}
```

# Call functions used in the homework for different questions

## Read data files and print summaries

```{r }
readFromFiles()
```

## Perform lm and plot digonistic plots 
```{r }
question1()
```
## Print summary of the lm and provide details of the p-value and slopes
```{r }
question2()
```

## Resolving lm residual assumption violations
```{r }
question3()
```

## Perform lm with missing data on complete cases 
```{r }
question4()
```
## Impute missing values using mice package and perform lm with new imputed values and compare with complete
```{r }
question5()
```
## Estimate the effect size for a given power of a test
```{r }
question6()
```

